
# Difference in resouce use betweek *H. curtus* and *H. schistosus*

Carbon and Nitrogen isotope ratios were compared across snake species. Plasma and scale samples were used to compare short term and long term resource use respectively. Multiples metrics including niche width (SEA), variance (range), overlap (%) were used.

<span style = "color: red;">**This section needs to be revised with new data from CEaS**</span>

```{r sia}

# importing stable isotope data

sia = read.csv("./Data/Stable Isotope Data_CEAS_241119.csv")

# joining SI data to snake data

sia_snakes = sia%>%
  filter(Tissue.type != "Gut Content")%>% # removing prey SI data
  left_join(snakes, 'Field.Code')%>%
  mutate(Lab = "CEAS")%>%
  # renamving variables for ease of understanding
  dplyr::rename(Delta.Carbon = d13C..vpdb. , Delta.Nitrogen = d15N..N2.air.)%>%
  # selecting relevant variables
  dplyr::select(Date, Field.Code, Species, Snout.to.Vent..cm., Sex, Gravid, Class,
                Gear.Type, Fishing.Location, Depth.Caught..m.,
                Plasma.Color, Delta.Carbon, Delta.Nitrogen, Lab, 
                Tissue.type, Month, Year)

# creating labels for figures

D.C = expression({delta}^13*C~'\u2030') 

D.N = expression({delta}^15*N~'\u2030')

```

## Number of tissue samples analysed 

```{r}

sia_snakes%>%
  filter(Tissue.type == "Plasma" | Tissue.type == "Scales")%>%
  filter(Species == "Hydrophis curtus" | Species == "Hydrophis schistosus")%>%
  group_by(Species, Tissue.type)%>%
  count()%>%
  spread(Tissue.type, n)

```

## Summary statistics on Carbon and Nitrogen stable isotopes

Mean ± standard deviation (parts per mil)

```{r}

sia_snakes%>%
  filter(Tissue.type == "Plasma" | Tissue.type == "Scales")%>%
  filter(Species == "Hydrophis curtus" | Species == "Hydrophis schistosus")%>%
  gather(c("Delta.Carbon", "Delta.Nitrogen"), key = "Isotope", value = "value")%>%
  group_by(Species, Tissue.type, Isotope)%>%
  summarise(Mean = round(mean(value, na.rm = T), 2),
            sd = round(sd(value, na.rm = T), 2),
            n = sum(!is.na(value)))%>%
  unite("Mean.sd", Mean:sd, sep = "±")%>%
  dplyr::select(-n)%>%
  spread(Isotope, Mean.sd)%>%
  arrange(Tissue.type, Species)

```

Both $\delta^{15}N$ and $\delta^{13}C$ were enriched in *H. schistosus* compared to _H. curtus_

## Difference in niche width between sea snakes

We used the SIBER package (Jackson et al. 2011) for to compare isotopic niche width and overlap between _H. curtus_ and _H. schistosus_. 

```{r, results = FALSE}

# importing required libraries for stable isotope analysis

library(SIBER)

# Formating SI data for use with SIBER

siber_snakes <- sia_snakes%>%
  dplyr::select(Delta.Carbon, Delta.Nitrogen, Tissue.type, Species)%>% # selecting required variables
  # renaming varibale as per requirement for SIBER
  dplyr::rename(iso1 = Delta.Carbon,
         iso2 = Delta.Nitrogen,
         group = Tissue.type,
         community = Species)%>%
  # removing missing data points
  filter(!is.na(group),
         !is.na(iso1),
         !is.na(iso2),
         community == "Hydrophis schistosus" | community == "Hydrophis curtus")%>%
  droplevels()

# Creating a SIBER object for analysis

siber.snakes = createSiberObject(siber_snakes)

```

### Maximum likelihood estimate of SEA

``` {r}

SEA.ML_snakes <- groupMetricsML(siber.snakes)

# Clean table 

data.frame(t(SEA.ML_snakes))%>%
  rownames_to_column("Species.Tissue")%>%
  separate(Species.Tissue, c("Species", "Tissue"), sep = "([\\.\\?\\:])")%>%
  arrange(Tissue, Species)

```

As maximum likelihood can only porivde point estimates of SEA, a bayesian model was used to provide more robust comparison of niche width.

<span style = "color: red;"> **Add comparisoon of ML SEA here** </span>

### Bayesian estimate of SEA

We estimate the standard ellipse area (SEA) of each species in isotopic space by fitting a multivaria normal model to the isotope data using bayesian inference.

```{r, results = FALSE}

# Setting options for running jags

parms <- list() # list of parameters fir JAGS

parms$n.iter <- 2*10^4   # number of iterations to run the model for

parms$n.burnin <- 1*10^3 # discard the first set of 1000 values

parms$n.thin <- 10 # thin the posterior by this many

parms$n.chains <- 2 # run this many chains

# Defining vague priors

priors <- list()

priors$R <- 1 * diag(2)

priors$k <- 2

priors$tau.mu <- 1.0E-3

# Fitting the model and getting posteriors

snakes.post <- siberMVN(siber.snakes, parms, priors)

# estimating standard ellipse area from posteriors

SEA.B_snakes <- siberEllipses(snakes.post)

# Creating a table of posterior estiamtes of Standard ellipse area

ccc <- names(snakes.post)

colnames(SEA.B_snakes) <- ccc

SEA.B_snakesdf = data.frame(SEA.B_snakes, check.names = F)%>%
  rowid_to_column(var = "run")%>%
  gather(Species.Tissue, SEA.B, -run)%>%
  separate(Species.Tissue, c("Species","Tissue"), sep = "([\\.\\?\\:])")
```

```{r}
# Summarising Bayesian estimate of SEA

SEA.B_snakesdf%>%
  group_by(Species, Tissue)%>%
  summarise(`Mean SEAb` = mean(SEA.B),
            `Standard deviation` = sd(SEA.B))%>%
  arrange(Tissue, Species)

```

<span style = "color: red;"> **Add comparisoon of Bayesian SEA here** </span>

### Testing difference in species niche area by tissue type

```{r}

SEA.B_snakesdf%>%
  spread(key = Species, value = SEA.B)%>%
  group_by(Tissue)%>%
  summarise(`P(HS > HC)` = sum(`Hydrophis schistosus` > `Hydrophis curtus`)/n())

```

Hypothesis: *H. schistosus* SEA is larger than *H. curtus*
  
While niche width is slightly larger in *H. schistosus*, it is not significantly different. The posterior distribution of SEA^~b~ has right skewed long tail (masked by the limits of the graph for visual clarity) possibly due to the low sample size. Niche width doesn't seem to change accross different tissue types either, indicating stability over variying periods of assimilation.

<span style = "color: red;"> **Update inference** </span>

## Visualising posterior ellipses to compare species isotopic niche

```{r fig.height=6}
# how many of the posterior draws do you want?

n.posts <- 10

# decide how big an ellipse you want to draw

p.ell <- pchisq(1,2)

set.seed(1)

# a list to store the results

snake_ellipses <- list()

# loop over groups

## generating list with length groups*communities

for (i in 1:length(snakes.post))
  {
  
  # a dummy variable to build in the loop
  
  ell <- NULL
  post.id <- NULL
  
  # randomly extracting parameters for n samples from posterior distribution
  
  for ( j in sample(1:4000, n.posts)){
    
    # covariance matrix
    
    Sigma <- matrix(snakes.post[[i]][j,1:4], 2, 2)
    
    # mean
    
    mu <- snakes.post[[i]][j,5:6]
    
    # ellipse points
    
    out <- ellipse::ellipse(Sigma, centre = mu , level = p.ell)
    
    
    ell <- rbind(ell, out) #ellipse points from current loop
    
    post.id <- c(post.id, rep(j, nrow(out))) #adding loop number (rep)
    
  }
  
  ell <- as.data.frame(ell) # data frame of ellipse points from all draws
  
  ell$rep <- post.id # adding draw id
  
  snake_ellipses[[i]] <- ell # creading list of draws from each community.group
}

snake.ellipses <- bind_rows(snake_ellipses, .id = "id") # creating a data frame of post ellipse draws


# now we need the group and community names

# extract them from the ellipses.posterior list

group_comm_names <- names(snakes.post)[as.numeric(snake.ellipses$id)] # extractin community.group from posteriors

# split them and conver to a matrix, NB byrow = T

split_group_comm <- matrix(unlist(strsplit(group_comm_names, "[.]")),
                           nrow(snake.ellipses), 2, byrow = TRUE) # splitting communit and group

snake.ellipses$community <- split_group_comm[,1]

snake.ellipses$group     <- split_group_comm[,2]

snake.ellipses <- dplyr::rename(snake.ellipses, iso1 = x, iso2 = y, Species = community, Tissue = group)

# Plotting 10 randomly sampled ellipses

siber_snakes%>%
  rename(Species = community,
         Tissue = group)%>%
  ggplot(aes(iso1, iso2, col = Species))+
  geom_point(aes(shape = Species), size = 2)+
  ylab(expression(paste(delta^{15}, "N (\u2030)")))+
  xlab(expression(paste(delta^{13}, "C (\u2030)")))+
  geom_polygon(data = snake.ellipses,
               mapping = aes(iso1, iso2, group = rep, linetype = Species, col = Species),
               fill = NA)+
  scale_color_grey()+
  facet_wrap(~Tissue)+
  theme(legend.text = element_text(face = "italic"))

ggsave(last_plot(), filename = "./Figures and Tables/figure3.tiff", height = 6, width = 8)
```

**Figure 3**: Bayesian ellipses in isotopic space describing difference in niche width and resource use between H. curtus and H. schistosus.

As seen in the SEA estimation, low sample size for *H. curtus* causes greater uncertainty in the estimation of standar ellipses even with bayesian inference. Both carbon and nitrogen isotpes seem to be enriched in scales when compared to plasma. Degree of overlap appears to be low for both tissues.

- Samples sizes for *H. curtus* in both tissues need to be increased despite using bayesian methods
- **Unusual outlier** in *H. schistosus* scales data needs to be checked

<span style = "color: red;"> **Update inference** </span>

## Relative overlap in bayesian standard ellipses

```{r, cache = TRUE}

# Overlap in ellipse based on plasma samples

snake.p.overlap <- bayesianOverlap(ellipse1 = "Hydrophis schistosus.Plasma" , #Group 1
                                   ellipse2 = "Hydrophis curtus.Plasma", #Group 2
                                   snakes.post, #list with posteriour dists
                                   draws = 100, p.interval = 0.95, n = 100) #params

snake.p.overlap <- snake.p.overlap%>%
  mutate(Turnover = "Short-term") # plasma represents short - term turnover in isotope ratios

# Overlap in ellipse based on scale samples

snake.s.overlap <- bayesianOverlap(ellipse1 = "Hydrophis schistosus.Scales" , #Group 1
                                   ellipse2 = "Hydrophis curtus.Scales", #Group 2
                                   snakes.post, #list with posteriour dists
                                   draws = 100, p.interval = 0.95, n = 100) #params

snake.s.overlap <- snake.s.overlap%>%
  mutate(Turnover = "Long-term") # scales represent long term turn over in isotope ratios

# Creating a combined data frame 

snake.overlap <- bind_rows(snake.p.overlap, snake.s.overlap)

# Plotting overlap

snake.overlap%>%
  mutate(prop.overlap = overlap/(area1 + area2 - overlap))%>% #relative overlap
  ggplot(aes(prop.overlap))+
  geom_histogram(bins = 10, col = "black")+
  #geom_vline(aes(xintercept = mean(prop.overlap),  col = "red"), size = 1)+
  labs(x = "Proportion of overlap", y = "Number of samples")+
  scale_color_discrete(name = "Mean")+
  facet_wrap(~Turnover)

```

```{r}

# summarising overlap in standard ellipses

snake.overlap%>%
  group_by(Turnover)%>%
  # calculating relative overlap in bayesian standard ellipses
  mutate(prop.overlap = overlap/(area1 + area2 - overlap))%>% 
  summarise(`Average overlap` = mean(prop.overlap),
            `Standard deviation` = sd(prop.overlap))

```

Overlap between *H. curtus* and *H. schistosus* seems to be high in when comparing long term resource use, i.e., scales.

However, overlap between *H. curtus* and *H. schistosus* seems to be very low when comparing short term resource use, i.e., plasma.

This difference could be caused by:

- low sample size for *H. curtus*
- differences in processing of scales and plasma, i.e., lipid extraction

<span style = "color: red;"> **Update inference** </span>

## References

- Section 4.3.2 was adapeted from [Andrew Jackson's Github example](https://github.com/AndrewLJackson/SIAR-examples-and-queries/blob/master/learning-resources/siber-comparing-populations.Rmd).

- Section 4.4 was adapted from the [SIBER Vignette](https://cran.r-project.org/web/packages/SIBER/vignettes/Plot-posterior-ellipses.html).

- Section 4.5 was adapted from this [Vignette](https://cran.r-project.org/web/packages/SIBER/vignettes/Ellipse-Overlap.html).
