# Varition in fishing intensity along the sindhudurg coast

```{r}
source("Functions/setup.R")

# importing effort data

effort = read.csv("./Data/Fishing-Effort_250720.csv")%>%
  group_by(Date, Gear.Type)%>%
  distinct(Boat.name, .keep_all = T)%>% # fixing repetitions in effort data
  mutate(Month = factor(months(dmy(Date)), 
                        levels = month.name),
         Year = year(dmy(Date)))%>%
  filter(Gear.Type == "Trawler" | Gear.Type == "GillNet") # removing beach seines and purse seines

```

## Calculating effort with depth

__Fishing intensity__: Vessel effort (Number of days fishing x No. of hauls x Average time per haul) is calculated for each boat on each day. This is then totaled for the sampling duration at each site.

- Should fishing intensity be analysed seperately by fishing gear.
- Should calculation of fishing intensity factor in Gears.


```{r echo = TRUE}

dep_int = effort%>% 
  filter(Fishing.Location != "")%>% #removing missing location data
  dplyr::select(Date, Gear.Type, Fishing.Location, Boat.name,
                No..of.Hauls, Average.Haul.Time..Hours., No..of.Days.fishing, Depth..wav.)%>%
  group_by(Gear.Type)%>%
  # interpolating missing data with medians
  mutate(n.days = ifelse(is.na(No..of.Days.fishing),
                         median(No..of.Days.fishing, na.rm = T), No..of.Days.fishing),
         n.hauls = ifelse(is.na(No..of.Hauls), 
                          median(No..of.Hauls, na.rm = T), No..of.Hauls),
         haul.time = ifelse(is.na(Average.Haul.Time..Hours.), 
                            median(Average.Haul.Time..Hours., na.rm = T), Average.Haul.Time..Hours.))%>%
  ungroup()%>%
  # calculating fihsing effort per trip
  mutate(effort = (n.days)*(n.hauls)*(haul.time),
         Depth.m = Depth..wav.*1.87)%>% # converting depth to meters
  dplyr::select(Date, Boat.name, Gear.Type, Fishing.Location, Depth.m, effort)%>% # selecting relevant variables
  drop_na() # remving missing values

```

## Geocoding fishing trips

Using data gathered from fisher surveys, we mapped the location of each fishing trip.

The protocol for geocoding fishing trips is as follows:

- Nearest landmarks are geocoded from google maps API 
- Latitude is extracted from landmark geocode
- Match landmark latitude and depth from survey to GEBCO data
- Extract final longitude from GEBCO data

The protocol is encoded in `Function/geocode.R`

```{r}

source("./Functions/geocode.R")

dep_int <- geocode.trips(dep_int, fl = 'Fishing.Location', dep = 'Depth.m')

# removing duplicates introduced by fuzzy joining

dep_int <- distinct(dep_int, Date, Boat.name, Fishing.Location, Gear.Type, Depth.m, .keep_all = T)

# savinf output

write.csv(dep_int, "./Data/Fishing intensity_dep.csv")

```

**Note:** `fuzzyjoin::fuzzy_inner_join()` introduces many duplicates, I have not as yet been able to fix the issue dirrectly. Currently, removing duplicates from output using `dplyr::distinct()`.


## No. of trips sampled

```{r}
## Sample size

knitr::kable(table(dep_int$Gear.Type))

```


## Summarising fishing effort per trip

```{r}

# effort per boat

dep_int%>%
  skimr::skim(effort)%>%
  skimr::yank("numeric")%>%
  dplyr::select(-hist)

```

## Testing difference in effort by gears

```{r}

# T - test

broom::tidy(t.test(effort ~ Gear.Type, data = dep_int))%>%
  dplyr::select(estimate:p.value)%>%
  # Effect size
  mutate(d = lsr::cohensD(effort ~ Gear.Type, data = dep_int))%>%
  dplyr::select(-estimate)%>%
  rename(`Gill net` = estimate1,
         Trawler = estimate2)

```

Trawlers had much higher fishing efforts than gillnets off the coast of Sindhudurg from 2018 - 2019.

## Mapping fishing intensity

```{r fp, fig.height=8}
# required libraries

library(sp)
library(rgdal)
library(raster)
library(ggmap)

# Sampling grid as raster

ext <- raster("./Data/sampling_extent.tif")

# importing functions for standardising effort

source("./Functions/intensity extract.R")
source("./Functions/raster to df.R")

# Calculating fishing intensity in each grid cell

fi <- dep_int%>%
  nest()%>%
  mutate(m = map(data, ~map.extract(df = ., var = "effort", func = 'sum')),
         mdf = map(m, map.df))%>%
  dplyr::select(mdf)%>%
  unnest()%>%
  rename(intensity = layer)

# Plotting intensity of fishing by gear type

base <- get_googlemap(center = c(mean(dep_int$lon),mean(dep_int$lat)), 
                      zoom = 9, scale = 4, maptype = "terrain")##Getting basemap

## importing bathymetric data downloaded from GEBCO database

library(marmap)

depth <- readGEBCO.bathy("./Data/gebco_2020_n16.7_s15.5_w72.0_e73.9.nc")

## converting depth data to usable data frame

depth = fortify.bathy(depth)%>%
  dplyr::rename(lon = x, lat = y, depth = z)%>%
  filter(depth < 1)

## creating plot
require(grid)
require(metR)
require(viridis)

ggmap(base)+
    metR::geom_contour2(data = depth, aes(x = lon, y = lat, z = depth),
                        breaks=seq(-10, -1000, -10), colour="black", size = 0.1, linetype = "dashed")+
    geom_tile(data = fi, aes(x = x, y = y, fill = intensity, alpha = intensity), color = "grey50")+
    coord_quickmap()+
    scale_x_continuous(limits = c(72.75, 73.75))+
    scale_y_continuous(limits = c(15.6, 16.6))+
    scale_fill_viridis(name = "Fishing intensity", option = "B", 
                       guide = guide_colorbar(direction = "horizontal",barwidth = 10, 
                                              title.position = "top", title.hjust = 0.5))+
    scale_alpha_continuous(range = c(0.7, 0.8), guide = F)+
    labs(x = "Longitude", y = "Latitude")+
    theme(legend.position = c(0.2, 0.9))

## saving high res figure for publication
 
ggsave(last_plot(), filename = "./Figures and Tables/figure4.tiff", width = 8, height = 8, dpi = 300)
```


**Figure 4**: Distribution of fishing intensity of trawlers in gillnets operating from Malvan, Maharashtra. Black lines indicate 10m depth contours

Each fishing trip is assigned to a cell in the sampling grid of **`r raster::ncell(ext)` cells** with **`r raster::nrow(ext)` rows** and **`r raster::ncol(ext)` columns**. Total fishing effort in each grid cell is then calculated to quatify local fishing intensity.

*Are points accurately depicted?*
  
Survey based map of fishing intensity may need to be verified with onboard observations and/or remote GPS data. Our field work for the same was cut short given the Coronavirus pandemic in 2020.

<span style = "color: red;"> **Link to prelimary results for fisheries mapping** </span>


## Spatial coverage of trawlers and gillnets along the Sindhudurg coast

```{r}


dep_int%>%
  nest()%>%
  ## Caluclating total effort in each grid cell
  mutate(m = map(data, ~map.extract(df = ., var = "effort", func = 'sum')),
         ## Converting raster to data frame
         mdf = map(m, map.df))%>%
  dplyr::select(mdf)%>%
  ## Caluclating spatial extent of fisheries as number of raster cells * 10 sq. km.
  summarise(`Extent (sq. km.)` = map(mdf, ~sum(.$layer>0)*10))%>%
  unnest()

```

As expexted, trawlers have a larger spatial foot print than gillnets.
