# Does isotopic niche of sea snakes change with local fishing intensity?

It is infeasible to to find sites with little to no fishing pressure on mainland India. Hence, it is nigh impossible to conduct a study with controls and test sites with varying levels of fishing pressure.

- How do you test the niche shift hypotheses with out spatial replicates?
  
  While the control - test study design failed, fishing effort data was collected from multiple vessels (Gillnet and Trawlers) landing at the Malvan harbour over the period of 1.5 years along side diet, abundance (snakes and prey), and isotopic data. So we ask the following questions:
  
  + Is there a corellation between fishing intensity and isotopic ratios?
  + Do niche metrics (width, overlap) vary with fishing pressure (high, medium and low preiods during the year)?
  
- What temporal resolution should be used for the analysis?
  
  - Day, week, month or season. 

- Which is appropriate and why?
  
  Depending on the tissue being analysed. Scales - month, Plasma - week

<span style = "color: red;"> **We used only plasma SI samples for this analysis as they reflect the isotopic assimilation in the short - term where effects of fisheries are expected.** </span>

## Determining cluster of fishing intensity off the coast of sindhudurg

We used hierarchical clustering based on fishing intensity of both gears, and the position of the cell in the grid to divided the grid into high and low fishing intensity zones. 

```{r fig.height=8, fig.width=8}
# loading required libraries

library(sp)
library(raster)

# importing data

dep_int <- read.csv("./Data/Fishing intensity_dep.csv") # geocoded fishing effort

snakes_den <- read.csv("./Data/snakes-density.csv") # sea snake occurence in bycatch

ext <- raster::raster("./Data/sampling_extent.tif") # sampling grid

# importing required scripts

source("./Functions/intensity extract.R")
source("./Functions/raster to df.R")

# Calculating fishing intensity

fi <- dep_int%>%
  group_by(Gear.Type)%>%
  nest()%>%
  mutate(m = map(data, ~map.extract(df = ., var = "effort", func = 'sum')),
         mdf = map(m, map.df))%>%
  dplyr::select(mdf)%>%
  unnest()%>%
  spread(Gear.Type, layer)

## creating distance matrix

dist_fi <- dist(fi)

## Hierarchical clustering

clust_fi <- hclust(dist_fi)

plot(clust_fi, hang = -1, labels = F)

## Assigning fishing intensity classes

fi_class <- cutree(clust_fi, k = 6) ## cutting the tree 4 times

## Naming clasess

fi <- fi%>%
  # extracting classes from clustering
  mutate(class = as.factor(ifelse(fi_class == 1 , "Low", "High")),
         fic = fi_class
         )%>%
  # reordering classes
  mutate(class = fct_relevel(class, c("High", "Medium", "Low")))
```


```{r fig.height=4, fig.width=4}
## Plotting grid

ggplot(fi, aes(x, y, fill = class))+
  geom_tile(col = "black")+
  scale_fill_brewer(palette = "Set1", name = "Fishing intensity")+
  labs(x = "Longitude", y = "Latitude")+
  theme(text = element_text(size = 10))
```

<span style = "color: red;"> **Clustering may need to be revised based on sample size** </span>

## Determining capture grid cell for individual snakes

Using data gathered from fisher surveys, we mapped the location of each fishing trip.

The protocol for geocoding fishing trips is as follows:

- Nearest landmarks are geocoded from google maps API 
- Latitude is extracted from landmark geocode
- Match landmark latitude and depth from survey to GEBCO data
- Extract final longitude from GEBCO data

The protocol is encoded in `Function/geocode.R`

```{r echo=TRUE}

# importing stable isotope data

sia = read.csv("./Data/Stable Isotope Data_CEAS_final_191020.csv")

# joining sia data to snake data

sia_snakes = sia%>%
  filter(Tissue.type == "Plasma" | Tissue.type == "Scales")%>%
  left_join(snakes, 'Field.Code')%>%
  mutate(Lab = "CEAS")%>%
  rename(Delta.Carbon = d13C..vpdb. , Delta.Nitrogen = d15N..N2.air.)%>%
  dplyr::select(Field.Code, Species, Snout.to.Vent..cm., Sex, Gravid, Class,
                Gear.Type, Fishing.Location, Location.encountered, Depth.Caught..m.,
                Plasma.Color, Delta.Carbon, Delta.Nitrogen, Lab, 
                Tissue.type, Month, Year)%>%
  # using location encountered where fishing location is unavailable
  mutate(Fishing.Location = ifelse(Fishing.Location == "", Location.encountered, Fishing.Location))%>%
  mutate(Fishing.Location = ifelse(Fishing.Location == "Dandi" | Fishing.Location == "Dandi Beach", "Wayari", Fishing.Location))

#selecting relavant variables

sia_li = sia_snakes%>%
  dplyr::select(Field.Code, Species, Fishing.Location, Depth.Caught..m.,Tissue.type,
                Delta.Carbon, Delta.Nitrogen)%>%
  filter(Fishing.Location != "")%>%
  drop_na()%>%
  droplevels()

## Geocoding si data

source("./Functions/geocode.R")

sia_li <- geocode.trips(sia_li, fl = 'Fishing.Location', dep = 'Depth.Caught..m.')

## removing duplicates introduced by fuzzy joining

sia_li <- distinct(sia_li, Field.Code, Tissue.type, .keep_all = T)


## Assigning grid cells to snakes

source("./Functions/find cell.R") # importing cell.ext function

ext <- raster::raster("./Data/sampling_extent.tif") # sampling grid

sia_fi <- sia_li%>%
  group_by(Field.Code, Species, Tissue.type, Delta.Carbon, Delta.Nitrogen)%>%
  nest()%>%
  mutate(cell = map(data, cell.ext),
         celldf = map(cell, as.data.frame))%>%
  dplyr::select(celldf)%>%
  unnest()%>%
  ungroup()

## Saving data to save time

write.csv(sia_li, "./Data/SIA_fishing intensity.csv")
```

**Note:** `fuzzyjoin::fuzzy_inner_join()` introduces many duplicates, I have not as yet been able to fix the issue dirrectly. Currently, removing duplicates from output using `dplyr::distinct()`.

## Sample size

```{r}


# adding fishing intensity class

sia_li <- sia_fi%>%
  left_join(fi, c("x","y"))%>%
  mutate(intensity = GillNet + Trawler)

# summarising number of samples

table(sia_li$Species, sia_li$Tissue.type, sia_li$class)%>%
  as.data.frame()%>%
  spread(Var3, Freq)%>%
  rename(Species = Var1,
         Tissue = Var2)%>%
  arrange(Species, Tissue)

```


## Variation isotope ratio with fishing intensity

```{r fig.height=8}

# plotting

sia_li%>%
  gather(key = Isotope, c(Delta.Carbon, Delta.Nitrogen), value = ratio)%>%
  ggplot(aes(intensity, ratio, col = Species))+
  geom_point(size = 3)+
  geom_smooth(method = lm)+
  scale_color_brewer(palette = "Set1")+
  labs(x = "Fishing intensity", y = "Isotope ratio")+
  theme(legend.text = element_text(face = "italic"))+
  facet_grid(Isotope ~ Tissue.type, scale = "free_y")

```

Both $\delta^{15}N$ and $\delta^{13}C$ show strong negatice relationship with increasing fishing intensity.

<span style = "color: red;"> **Update with new SI data** </span>

## Modeling isotope ratios with fishing intensity

```{r}

sia_li%>%
  gather(key = Isotope, c(Delta.Carbon, Delta.Nitrogen), value = ratio)%>%
  group_by(Species, Isotope, Tissue.type)%>%
  nest()%>%
  mutate(
    mod1 = map(data, ~lm(ratio ~ intensity, data = .)),
    summ1 = map(mod1, broom::tidy),
    r2 = map(mod1, broom::glance)
  )%>%
  dplyr::select(summ1, r2)%>%
  unnest()%>%
  dplyr::select(Species:p.value, adj.r.squared)%>%
  arrange(Species, Tissue.type, adj.r.squared) -> sia_fi_lm

library(knitr)
library(kableExtra)

sia_fi_lm <- sia_fi_lm%>%
  rename(`Tissue type` = Tissue.type,
         Parameter = term,
         Coefficient = estimate,
         `Standard Error` = std.error,
         `T` = statistic,
         p = p.value,
         `r_adj^2` = adj.r.squared
         )%>%
  mutate(Parameter = ifelse(Parameter == "(Intercept)", "Intercept", "Fishing intensity"),
         `T` = ifelse(Parameter == "Intercept", NA, `T`),
         p = ifelse(Parameter == "Intercept", NA, p))

kbl(sia_fi_lm, booktabs = T, digits = 3)%>%
  column_spec(1, italic = T)%>%
  collapse_rows(columns = 1:3, row_group_label_position ='stack')
```

Samples sizes for *H. curtus* are low, however, fishing intensity seems to have a significant __depletion effect__ on plasma isotope ratios in _H. schistosus_.

## Difference in niche width between sea snakes

See section 4 for more details on analysis with SIBER.

```{r, results = FALSE}

# Loading required libraries

library(SIBER)

#Creating siber data

## Plasma samples

siber_pl_fi = sia_li%>%
  filter(Tissue.type == "Plasma")%>% # using plasma values for comparison
  dplyr::select(Delta.Carbon, Delta.Nitrogen, Species, class)%>%
  # renaming baed on SIBER conventions
  rename(iso1 = Delta.Carbon,
         iso2 = Delta.Nitrogen,
         group = class, # setting fishing intesnity as group
         community = Species)%>%
  # removing missing data
  filter(!is.na(group),
         !is.na(iso1),
         !is.na(iso2),
         community == "Hydrophis schistosus" | community == "Hydrophis curtus")%>%
  ungroup()%>%
  dplyr::select(iso1, iso2, group, community)%>%
  droplevels()

# Creating SIBER object fo MVN fitting

siber.plasma.fi = createSiberObject(as.data.frame(siber_pl_fi))

## Scale samples

siber_sc_fi = sia_li%>%
  filter(Tissue.type == "Scales")%>% # using plasma values for comparison
  dplyr::select(Delta.Carbon, Delta.Nitrogen, Species, class)%>%
  # renaming baed on SIBER conventions
  rename(iso1 = Delta.Carbon,
         iso2 = Delta.Nitrogen,
         group = class, # setting fishing intesnity as group
         community = Species)%>%
  # removing missing data
  filter(!is.na(group),
         !is.na(iso1),
         !is.na(iso2),
         community == "Hydrophis schistosus" | community == "Hydrophis curtus")%>%
  ungroup()%>%
  dplyr::select(iso1, iso2, group, community)%>%
  droplevels()

# Creating SIBER object fo MVN fitting

siber.scales.fi = createSiberObject(as.data.frame(siber_sc_fi))

```

### Maximum likelihood estimate of SEA

``` {r}

SEA.ML_plasma.fi <- groupMetricsML(siber.plasma.fi)# for plamsa samples

SEA.ML_scales.fi <- groupMetricsML(siber.scales.fi)# for scale samples

data.frame(t(SEA.ML_plasma.fi))%>%
  rownames_to_column("Species.FI")%>%
  mutate(Tissue = "Plasma")%>%
  full_join(
    (data.frame(t(SEA.ML_scales.fi))%>%
  rownames_to_column("Species.FI")%>%
  mutate(Tissue = "Scales")
  )
  )%>%
  group_by(Tissue)%>%
  arrange(Species.FI)


```

As maximum likelihood can only porivde point estimates of SEA, a bayesian model was used to provide more robust comparison of niche width.

### Bayesian estimate of SEA

```{r, results = FALSE}

# options for running jags
parms <- list()
parms$n.iter <- 2 * 10^4   # number of iterations to run the model for
parms$n.burnin <- 1 * 10^3 # discard the first set of values
parms$n.thin <- 10     # thin the posterior by this many
parms$n.chains <- 2        # run this many chains

# define the priors
priors <- list()
priors$R <- 1 * diag(2)
priors$k <- 2
priors$tau.mu <- 1.0E-3

# scale samples

scales.fi.post <- siberMVN(siber.scales.fi, 
                           parms, priors)#fitting multivariate normal model and getting                                                          posteriors

SEA.B_scales.fi <- siberEllipses(scales.fi.post)#estimating standard ellipse area from posteriors

means.B_scales.fi <- extractPosteriorMeans(siber.scales.fi, scales.fi.post)#mean isotope values

ccc <- names(scales.fi.post)

colnames(SEA.B_scales.fi) <- ccc

# plasma samples

plasma.fi.post <- siberMVN(siber.plasma.fi, 
                           parms, priors)#fitting multivariate normal model and getting                                                          posteriors

SEA.B_plasma.fi <- siberEllipses(plasma.fi.post)#estimating standard ellipse area from posteriors

means.B_plasma.fi <- extractPosteriorMeans(siber.plasma.fi, plasma.fi.post)#mean isotope values

ccc <- names(plasma.fi.post)

colnames(SEA.B_plasma.fi) <- ccc

# creating data frame

SEA.B_snakes.fi.df = data.frame(SEA.B_plasma.fi, check.names = F)%>%
  rowid_to_column(var = "run")%>%
  gather(Species.class, SEA.B, -run)%>%
  separate(Species.class, c("Species","FI.Class"), sep = "([\\.\\?\\:])")%>%
  mutate(Tissue = "Plasma")%>%
  # appending scale runs
  full_join(
    data.frame(SEA.B_scales.fi, check.names = F)%>%
      rowid_to_column(var = "run")%>%
      gather(Species.class, SEA.B, -run)%>%
      separate(Species.class, c("Species","FI.Class"), sep = "([\\.\\?\\:])")%>%
      mutate(Tissue = "Scale")
  )

```

```{r}

#Summarising SEA estimates

SEA.B_snakes.fi.df%>%
  group_by(Species, Tissue, FI.Class)%>%
  summarise(SEA.mean = mean(SEA.B),
            SEA.sd = sd(SEA.B),
            SEA.se = sd(SEA.B)/sqrt(n()))

```

### Testing difference in species niche area by fishing intensity

```{r}

SEA.B_snakes.fi.df%>%
  spread(key = FI.Class, value = SEA.B)%>%
  group_by(Species, Tissue)%>%
  summarise(`P(High > Low)` = sum(`High` > `Low`)/n())
            #Currently no medium cells
            #`P(Medium > Low)` = sum(`Medium` > `Low`)/n(), 
            #`P(High > Medium)` = sum(`High` > `Medium`)/n())

```

### Visualising difference in niche width across gradiet of fishing intensity

```{r fig.height=6, fig.width=10}
library(gridExtra)

SEA.B_snakes.fi.df%>%
  # reordering classes
  mutate(FI.Class = fct_relevel(FI.Class, c("High", "Medium", "Low")))%>%
  ggplot(aes(Species, SEA.B, fill = FI.Class))+
  geom_violin(alpha = 0.3, position = position_dodge(0.4), width = 0.5)+
  geom_boxplot(alpha = 0.3, width = 0.05, outlier.alpha = 0, position = position_dodge(0.4))+
  scale_y_continuous(name = "Standard Ellispes Area", guide = guide_axis(n.dodge = 1))+
  scale_fill_discrete(name = "Fishing Intensity")+
  facet_wrap(~Tissue)+
  theme(axis.text.x = element_text(face = "italic"))

ggsave(last_plot(), filename = "./Figures and Tables/figure6.png", height = 6, width = 10, device = "png")

```

Currently many outliers from 5 - 15 on y - axis