# Difference in diet by sex within *H. curtus* and *H. schsistosus*

```{r}
source("./Functions/setup.R")

gc = read.csv("./Data/Sea_snakes_gut_content_2018-19.csv")%>%
  filter(Source == "Gut content") # removing specimens collected from fisheries landings
```

The number of samples for conducting a sex wise analysis of feeding preference is limited for *H. curtus*.

## Prey Preference

We modified and used the the Index of relative importance according to Pinkas et al. 1971 to determine the difference in prey preference between males and females in _H. curtus_ and _H. schistosus_

```{r}
# calulating index of relative importance (Pinkas et al. 1971)

IRI_sex <- gc%>%
  left_join(snakes, by = c("Field.Code"))%>%
  filter(Prey.Family != "", Sex != "", Snake.Species == "Hydrophis schistosus" | Snake.Species == "Hydrophis curtus")%>%
  group_by(Snake.Species, Sex)%>%
  mutate(Fr = length(unique(Field.Code)), # total number of snakes sampled
         W = sum(Weight..g..x, na.rm = T), # total weight of prey sampled
         N = n())%>% # total number of prey sampled
  group_by(Snake.Species, Sex, Prey.Family)%>%
  summarise(f = length(unique(Field.Code)), # number snakes in which prey family occured
            Fr = last(Fr),
            w = sum(Weight..g..x, na.rm = T), # weight of prey family
            W = last(W),
            n = n(), # number of individuals of prey family
            N = last(N))%>%
  group_by(Snake.Species, Sex, Prey.Family)%>%
  # caluclating percentages
  summarise(per.F = f*100/Fr,
            per.W = w*100/W,
            per.N = n*100/N,
            # caluclating IRI
            IRI = (per.N + per.W)*per.F)%>%
  arrange(Snake.Species, Sex, desc(IRI))%>%
  mutate(rank = 1:n())

# clean table

IRI_sex
```

```{r fig.height=8, fig.width=8}

# plotting prey preference

IRI_sex%>%
  ggplot(aes(Prey.Family, IRI, fill = Sex))+
  geom_col(col = "black", position = position_dodge(preserve = "single"))+
  scale_y_sqrt(name = "IRI (sq.rt.)")+
  labs(x = "Prey Family")+
  scale_fill_brewer(palette = "Greys", name = "Snake Species")+
  theme(axis.text.x = element_text(hjust = 1, angle = 60),
        strip.text = element_text(face = "italic"))+
  facet_wrap(~Snake.Species, ncol = 1)
```


## Range of prey found in _H. curtus_ and _H. shistosus_ gut

We compared the dietary breadth between snakes species using the richness and diversity of prey families.

```{r}

# Creating data matrix for prey community analysis analysis

fam_spade_sex = gc%>%
  left_join(snakes, by = c("Field.Code"))%>%
  filter(Prey.Family != "Unidentified", Prey.Family !="", Field.Code != "", Sex != "")%>% # removing unidentified specimens
  group_by(Snake.Species, Sex, Prey.Family)%>%
  summarise(n = n())%>% # total number of specimens per family in each snake species
  unite("Species_sex", Snake.Species:Sex)%>%
  spread(Species_sex, n, fill = 0)%>%
  column_to_rownames("Prey.Family")


```

### Prey richness

```{r}

gc%>%
  left_join(snakes, by = c("Field.Code"))%>%
  filter(Snake.Species == "Hydrophis schistosus" | Snake.Species == "Hydrophis curtus",
         Prey.Family != "Unidentified", Prey.Family != "", Sex != "")%>%
  group_by(Snake.Species, Sex)%>%
  summarise(Prey.Species = length(unique(Prey.Species)) - 1, # removing unidentified
            Prey.Families = length(unique(Prey.Family)))

```

### Prey family diversity

```{r}

# loading libraries

library(SpadeR) ## for community indices

# calculating shanon diversity

#HC_f_div = as.data.frame(Diversity(fam_spade_sex[,1])$Shannon_diversity)%>%
 # rownames_to_column("Estimator")%>%
  #mutate(Species = "Hydrophis curtus",
    #     Sex = "Female")

#HC_m_div = as.data.frame(Diversity(fam_spade_sex[,2])$Shannon_diversity)%>%
 # rownames_to_column("Estimator")%>%
  #mutate(Species = "Hydrophis curtus",
   #      Sex = "Male")

HS_f_div = as.data.frame(Diversity(fam_spade_sex[,3])$Shannon_diversity)%>%
  rownames_to_column("Estimator")%>%
  mutate(Species = "Hydrophis schistosus",
         Sex = "Female")

HS_m_div = as.data.frame(Diversity(fam_spade_sex[,4])$Shannon_diversity)%>%
  rownames_to_column("Estimator")%>%
  mutate(Species = "Hydrophis schistosus",
         Sex = "Male")

HS_m_div%>%
  full_join(HS_f_div)%>%
  dplyr::select(Species, Sex, everything())%>%
  arrange(Estimator)
```

While _H. schistosus_ fed on greater number of prey families, _H. curtus_ showed greater evenness in prey preference.

Statistical comparison is difficult as each individual snake fed on only one type of specimen at time.

## Diet overlap between Males and Females

Number of overlapping prey families:

```{r}

gc%>%
  left_join(snakes, by = "Field.Code")%>%
  filter(Snake.Species == "Hydrophis schistosus" | Snake.Species == "Hydrophis curtus",
         Prey.Family != "Unidentified", Prey.Family != "", Sex != "")%>%
  group_by(Snake.Species, Prey.Family)%>%
  summarise(N_pred = length(unique(Sex)))%>%
  group_by(Snake.Species)%>%
  summarise(Overlap = sum(N_pred>1))

```

Morista - Horn overlap for *Hydrophis schistosus*:

```{r}
prey_sim_HS <- SimilarityPair(X = fam_spade_sex[,3:4], datatype = "abundance")

as.data.frame(prey_sim_HS$Empirical_relative)
```

There was high overlap in prey between males and females in _H. schistosus_.

Morista - Horn overlap for *Hydrophis schistosus*:

```{r}
#prey_sim_HC <- SimilarityPair(X = fam_spade_sex[,1:2], datatype = "abundance")

#prey_sim_HC$Empirical_relative
```

Very low sample size.

### Testing segregation in prey between sexes

```{r}
# loading libraries

library(vegan)

# formating data for vegan

fam_simboo_sex <- gc%>%
  left_join(snakes, by = "Field.Code")%>%
  filter(Prey.Family != "Unidentified", Prey.Family !="", Field.Code != "", Sex != "")%>%
  group_by(Snake.Species, Sex, Field.Code, Prey.Family)%>%
  summarise(n = n())%>%
  spread(Prey.Family, n, fill = 0)%>%
  ungroup()
```

*H. curtus*:

```{r}
# PERMANOVA to compare composition

set.seed(2)

permanova_hc <- adonis2(fam_simboo_sex[1:14,4:length(fam_simboo_sex)] ~ fam_simboo_sex[1:14,]$Sex,
                     data = fam_simboo_sex[1:14,2])
## clean table

broom::tidy(permanova_hc)
```

No difference in prey preference, however, sample sizes are low.

*H. schistosus*:

```{r}
permanova_hs <- adonis2(fam_simboo_sex[15:69,4:length(fam_simboo_sex)] ~ fam_simboo_sex[15:69,]$Sex,
                     data = fam_simboo_sex[15:69,2])
## clean table

broom::tidy(permanova_hc)
```

No difference in prey preference across species.

## Difference in size selectivity of prey between _H. curtus_ and _H. schistosus_

```{r}

# summary

gc%>%
  left_join(snakes, by = c("Field.Code"))%>%
  filter(Snake.Species == "Hydrophis schistosus" | Snake.Species == "Hydrophis curtus", Sex != "",
         Condition < 3)%>% # removing very digested specimens 
  group_by(Snake.Species, Sex)%>%
  skimr::skim(Maximum.Body.Girth..cm.)%>%
  skimr::yank("numeric")%>%
  dplyr::select(Snake.Species:p100)


# testing diff max prey width by species

gc%>%
  left_join(snakes, by = c("Field.Code"))%>%
  filter(Snake.Species == "Hydrophis schistosus" | Snake.Species == "Hydrophis curtus", Sex != "",
         Condition < 3, # removing very digested specimens  
         !is.na(Maximum.Body.Girth..cm.))%>% # removing unrecorded data
  dplyr::select(Snake.Species, Sex, Maximum.Body.Girth..cm.)%>%
  droplevels()%>%
  group_by(Snake.Species)%>%
  nest()%>%
  mutate(test = map(data, ~t.test(Maximum.Body.Girth..cm. ~ Sex, data = .)), # t test
         sumry = map(test, broom::tidy),
         d = map(data, ~lsr::cohensD(Maximum.Body.Girth..cm. ~ Sex, data = .)))%>% # effect size
  dplyr::select(sumry, d)%>%
  unnest()%>%
  dplyr::select(estimate1:parameter, d)%>%
  rename(`Females` = estimate1,
         `Males` = estimate2)
```

There were no significant differences in prey girth across sexes in both species. However, females did take slightly larger prey in both cases.
