---
title: "Resouce use in two sympatric species of sea snakes in anthropogenically dominated seascape"
output:
  html_document:
    css: style.css
    df_print: kable
    theme: spacelab
    toc: yes
    toc_float: yes
    toc_depth: 2
    number_sections: yes
    code_folding: hide
subtitle: Analysis for manuscript
Author: Shawn Dsouza, Chetan Rao, Muralidharan M., and Kartik Shanker
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}

# setting global opitions

options(max.print="75")

knitr::opts_chunk$set(echo = T, error = T, warning = F, message = F, tidy = T, 
                      cache = T,
                      dpi = 300, fig.align = "center")

# Required libraries

library(tidyverse)
library(lubridate)

# Data import

snakes = read.csv("./Data/Sea-snakes_fish-dep_2018-19_070220.csv")

# setting ggplot theme

theme_set(theme_bw()+
            theme(legend.position = "top",
                  text = element_text(size = 20)
                  )
          )
```


# Introduction

This file contains the code for analysis in R for a study about resources use in sea snakes on the west coast of India. 

The core message of this manuscripts are as follows:

- Resource use differs between _H. curtus_ and _H. schistosus_
- Variation in fishing intensity of trawlers and gillnets affects patterns of resource use

We used a combination of approaches including: 

a. fisheries dependent methods to characterise distribution and habitat use of the two species, and spatial overlap with fishing; 

b. visual gut content analysis to characterise diet and trophic niche of the species, and overlap between fisheries catch and sea snake diet; 

c. stable isotope analysis to characterise overall resource use in terms of isotopic niche, as well as the effect of fishing intensity on the niche width of both species.

This file was last update on `r Sys.Date()`

```{r child = './Sections/Fishing intensity.rmd'}
```

```{r child = './Sections/Habitat use.rmd'}
```

```{r child = './Sections/Diet.rmd'}
```

```{r child = './Sections/Isotopic Niche.rmd'}
```

```{r child = './Sections/Fisheries - spatial overlap.rmd'}
```

```{r child = './Sections/Fisheries - diet overlap.rmd'}
```

```{r child = './Sections/Fisheries - isotopic niche.rmd'}
```
