---
title: "Resouce use in two sympatric species of sea snakes in anthropogenically dominated seascape"
output:
  html_document:
  css: style.css
df_print: kable
theme: spacelab
toc: yes
toc_float: yes
toc_depth: 2
number_sections: yes
subtitle: Fisheries - isotopic niche
Author: Shawn Dsouza
---

# Does isotopic niche of sea snakes change with local fishing intensity?

As it is infeasible to to find sites with little to no fishing pressure on mainland India. The ultimate objective of this project remains unfulfilled it is nigh impossible to conduct a study with controls and test sites with varying levels of fishing pressure.

- How do you test the niche shift hypotheses with out spatial replicates?
  
  While the control - test study design failed, fishing effort data was collected from multiple vessels (Gillnet and Trawlers) landing at the Malvan harbour over the period of 1.5 years along side diet, abundance (snakes and prey), and isotopic data. So we ask the following questions:
  
  + Is there a corellation between fishing intensity and isotopic ratios?
  + Do niche metrics (width, overlap) vary with fishing pressure (high, medium and low preiods during the year)?
  
  What temporal resolution should be used for the analysis?
  
  - Day, week, month or season. 
- Which is appropriate and why?
  
  Depending on the tissue being analysed. Scales - month, Plasma - week

- What are the existing data and sampling structures and what can be improved?

```{r}
# determining clusters for fishing intensity

fi_den <- read.csv("./data/cell_fish_snake.csv")

fi_den = fi_den%>%
  mutate(id = 1:nrow(fi_den))

fi = fi_den%>%
  dplyr::select(id, x, y, GillNet, Trawler)

dist_fi <- dist(fi)

clust_fi <- hclust(dist_fi)

fi_class <- cutree(clust_fi, 3)

fi <- fi%>%
  mutate(class = as.factor(ifelse(fi_class == 2, "High", "Low")))

ggplot(fi, aes(x, y, fill = class))+
  geom_tile()
```

```{r, eval=FALSE, echo=TRUE}
#Stable isotope data

sia = read.csv("./Data/Stable Isotope Data_CEAS_241119.csv")

#joining sia data to snake data

sia_snakes = sia%>%
  filter(Tissue.type != "Gut Content")%>%
  left_join(snakes, 'Field.Code')%>%
  mutate(Lab = "CEAS")%>%
  rename(Delta.Carbon = d13C..vpdb. , Delta.Nitrogen = d15N..N2.air.)%>%
  dplyr::select(Date, Field.Code, Species, Snout.to.Vent..cm., Sex, Gravid, Class,
                Gear.Type, Fishing.Location, Depth.Caught..m.,
                Plasma.Color, Delta.Carbon, Delta.Nitrogen, Lab, 
                Tissue.type, Month, Year)

#selecting relavant variables

sia_fi = sia_snakes%>%
  dplyr::select(Field.Code, Species, Fishing.Location, Depth.Caught..m.,Tissue.type,
                Delta.Carbon, Delta.Nitrogen)%>%
  filter(Fishing.Location != "")%>%
  drop_na()%>%
  droplevels()

# Geocoding capture location

sia_fi <- sia_fi%>%
  ungroup()%>%
  mutate(Fishing.Location = as.character(Fishing.Location))%>%
  mutate_geocode(location = Fishing.Location)

# Extracting coordinates from depth data

library(fuzzyjoin)

#matching funtions for theta join

depth_match <- function(x,y){
  x <- -x
  x <= y+0.5 & x >= y-0.5 #interval for theta matching depth
}

lat_match <- function(x,y){
  x <= y+0.005 & x >= y-0.005 #interval for theta matching latitude
}

sia_fi <- sia_fi%>%
  mutate(depth = Depth.Caught..m.)%>%
  fuzzy_inner_join(y = depth, by = c("depth", "lat"), 
                   match_fun = list(depth = depth_match,
                                    lat = lat_match))%>%
  dplyr::select(Field.Code, Species, Fishing.Location, Depth.Caught..m., Tissue.type,
                Delta.Carbon, Delta.Nitrogen, lon.y, lat.x)%>%#dplyr::selecting relevant variables
  rename(lon = lon.y,# longitude from fishing location
         lat = lat.x)%>%# latitude from depth data
  distinct(Field.Code, Tissue.type, .keep_all = T)

# Finding grid cell in which snake was captured

cell.ext <- function(df){
  
  r <- raster::projectRaster(ext, crs = CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))
  
  xy <- df
  
  coordinates(xy) <- ~lon + lat
  
  proj4string(xy) <- CRS("+init=epsg:4326")#setting projection to WGS 84 (lon/lat)
  
  #xy <- spTransform(xy, CRSobj = CRS("+init=epsg:3857"))#using spherical mercator
  
  c <- xyFromCell(r, cellFromXY(r, xy))
  
}

sia_li <- sia_fi%>%
  group_by(Field.Code, Species, Tissue.type, Delta.Carbon, Delta.Nitrogen)%>%
  nest()%>%
  mutate(cell = map(data, cell.ext),
         celldf = map(cell, as.data.frame))%>%
  dplyr::select(celldf)%>%
  unnest()%>%
  inner_join(fi, by = c("x", "y"))

write.csv(sia_li, "./Data/SIA_fishing intensity.csv")
```


## Sample size

```{r}
sia_li <- read.csv("./Data/SIA_fishing intensity.csv")

sia_li <- sia_li%>%
  inner_join(fi, c("x","y"))

table(sia_li$Species, sia_li$Tissue.type)
```


## Variation Carbon isotope ratio with fishing intensity

```{r}
sia_li%>%
  filter(Tissue.type == "Plasma")%>%
  gather(key = Isotope, c(Delta.Carbon, Delta.Nitrogen), value = ratio)%>%
  ggplot(aes(intensity, ratio))+
  geom_point(size = 3)+
  geom_smooth(method = lm)+
  labs(x = "Fishing intensity")+
  theme(legend.text = element_text(face = "italic"))+
  facet_wrap(~Isotope, scale = "free_y")
```


## Modeling isotope ratios with fishing intensity

### Continous model

```{r}
sia_li%>%
  filter(Tissue.type == "Plasma")%>%
  gather(key = Isotope, c(Delta.Carbon, Delta.Nitrogen), value = ratio)%>%
  group_by(Species, Isotope)%>%
  nest()%>%
  mutate(
    mod1 = map(data, ~lm(ratio ~ intensity, data = .)),
    summ1 = map(mod1, tidy),
    anova = map(mod1, car::Anova), 
    r2 = map(mod1, broom::glance)
  )%>%
  dplyr::select(summ1, r2)%>%
  unnest()%>%
  dplyr::select(Species:p.value, adj.r.squared)
```

Samples sizes for *H. curtus* are low, however, fishing intensity seems to have a significant __depletion effect__ on plasma isotope ratios in _H. schistosus_.

## Difference in niche width between sea snakes

```{r, results = FALSE}
library(SIBER)

#Creating siber data
siber_fi = sia_li%>%
  filter(Tissue.type == "Plasma")%>%
  dplyr::select(Delta.Carbon, Delta.Nitrogen, Species, class)%>%
  rename(iso1 = Delta.Carbon,
         iso2 = Delta.Nitrogen,
         group = class,
         community = Species)%>%
  filter(!is.na(group),
         !is.na(iso1),
         !is.na(iso2),
         community == "Hydrophis schistosus" | community == "Hydrophis curtus")%>%
  ungroup()%>%
  dplyr::select(iso1, iso2, group, community)%>%
  droplevels()

siber.snakes.fi = createSiberObject(as.data.frame(siber_fi))
```

### Maximum likelihood estimate of SEA

``` {r}
SEA.ML_snakes.fi <- groupMetricsML(siber.snakes.fi) #maximum likelihood estimates

data.frame(t(SEA.ML_snakes.fi))

```

As maximum likelihood can only porivde point estimates of SEA, a bayesian model was used to provide more robust comparison of niche width.

### Bayesian estimate of SEA

```{r, results = FALSE}
# options for running jags
parms <- list()
parms$n.iter <- 2 * 10^4   # number of iterations to run the model for
parms$n.burnin <- 1 * 10^3 # discard the first set of values
parms$n.thin <- 10     # thin the posterior by this many
parms$n.chains <- 2        # run this many chains

# define the priors
priors <- list()
priors$R <- 1 * diag(2)
priors$k <- 2
priors$tau.mu <- 1.0E-3

snakes.fi.post <- siberMVN(siber.snakes.fi, 
                           parms, priors)#fitting multivariate normal model and getting                                                          posteriors

SEA.B_snakes.fi <- siberEllipses(snakes.fi.post)#estimating standard ellipse area from posteriors

means.B_snakes.fi <- extractPosteriorMeans(siber.snakes.fi, snakes.fi.post)#mean isotope values

ccc <- names(snakes.fi.post)

colnames(SEA.B_snakes.fi) <- ccc

SEA.B_snakes.fi.df = data.frame(SEA.B_snakes.fi, check.names = F)%>%
  rowid_to_column(var = "run")%>%
  gather(Species.class, SEA.B, -run)%>%
  separate(Species.class, c("Species","FI.Class"), sep = "([\\.\\?\\:])")

```

```{r}
#Summarising SEA estimates

SEA.B_snakes.fi.df%>%
  group_by(Species, FI.Class)%>%
  summarise(SEA.mean = mean(SEA.B),
            SEA.sd = sd(SEA.B),
            SEA.se = sd(SEA.B)/sqrt(n()))

```

### Testing difference in species niche area by tissue type

```{r}
SEA.B_snakes.fi.df%>%
  spread(key = FI.Class, value = SEA.B)%>%
  group_by(Species)%>%
  summarise(p = sum(`High` > `Low`)/n())
```

```{r}
SEA.B_snakes.fi.df%>%
  ggplot(aes(Species, SEA.B, fill = FI.Class))+
  geom_boxplot(alpha = 0.3, width = 0.25)+
  scale_y_continuous(limits = c(0,20), name = "Standard Ellispes Area")+
  scale_fill_discrete(name = "Fishing Intensity")+
  theme(axis.text.x = element_text(face = "italic"))

ggsave(last_plot(), filename = "./Figures/fig6.png", height = 4.5, width = 8, device = "png")
```

