
# Difference in resouce use betweek *H. curtus* and *H. schistosus*?

Carbon and Nitrogen isotope ratios were compared accorss species. Plasma and scale samples were used to compare short term and long term resource use respectively. Multiples metrics including niche width (SEA), variance (range), overlap (%) were used.

```{r sia}
#Stable isotope data
sia = read.csv("../Data/Stable Isotope Data_CEAS_241119.csv")

#joining sia data to snake data

sia_snakes = sia%>%
  filter(Tissue.type != "Gut Content")%>%
  left_join(snakes, 'Field.Code')%>%
  mutate(Lab = "CEAS")%>%
  dplyr::rename(Delta.Carbon = d13C..vpdb. , Delta.Nitrogen = d15N..N2.air.)%>%
  dplyr::select(Date, Field.Code, Species, Snout.to.Vent..cm., Sex, Gravid, Class,
                Gear.Type, Fishing.Location, Depth.Caught..m.,
                Plasma.Color, Delta.Carbon, Delta.Nitrogen, Lab, 
                Tissue.type, Month, Year)

#labels

D.C =expression({delta}^13*C~'\u2030') 

D.N =expression({delta}^15*N~'\u2030')


```

## Number of samples analysed 

```{r}
sia_snakes%>%
  filter(Tissue.type == "Plasma" | Tissue.type == "Scales")%>%
  filter(Species == "Hydrophis curtus" | Species == "Hydrophis schistosus")%>%
  group_by(Species, Tissue.type)%>%
  count()%>%
  spread(Tissue.type, n)
```

## Summary statistics on Carbon and Nitrogen stable isotopes

```{r}
sia_snakes%>%
  filter(Tissue.type == "Plasma" | Tissue.type == "Scales")%>%
  filter(Species == "Hydrophis curtus" | Species == "Hydrophis schistosus")%>%
  gather(c("Delta.Carbon", "Delta.Nitrogen"), key = "Isotope", value = "value")%>%
  group_by(Species, Tissue.type, Isotope)%>%
  summarise(Mean = round(mean(value, na.rm = T), 2),
            sd = round(sd(value, na.rm = T), 2),
            n = sum(!is.na(value)))%>%
  unite("Mean.sd", Mean:sd, sep = "±")%>%
  dplyr::select(-n)%>%
  spread(Isotope, Mean.sd)
```

## Difference in niche width between sea snakes

```{r, results = FALSE}
library(SIBER)

#Creating siber data
siber_snakes = sia_snakes%>%
  filter()%>%
  dplyr::select(Delta.Carbon, Delta.Nitrogen, Tissue.type, Species)%>%
  dplyr::rename(iso1 = Delta.Carbon,
         iso2 = Delta.Nitrogen,
         group = Tissue.type,
         community = Species)%>%
  filter(!is.na(group),
         !is.na(iso1),
         !is.na(iso2),
         community == "Hydrophis schistosus" | community == "Hydrophis curtus")%>%
  droplevels()

siber.snakes = createSiberObject(siber_snakes)
```

### Maximum likelihood estimate of SEA

``` {r}
SEA.ML_snakes <- groupMetricsML(siber.snakes) #maximum likelihood estimates

data.frame(t(SEA.ML_snakes))

```

As maximum likelihood can only porivde point estimates of SEA, a bayesian model was used to provide more robust comparison of niche width.

### Bayesian estimate of SEA

```{r, results = FALSE}
# options for running jags
parms <- list()
parms$n.iter <- 2 * 10^4   # number of iterations to run the model for
parms$n.burnin <- 1 * 10^3 # discard the first set of values
parms$n.thin <- 10     # thin the posterior by this many
parms$n.chains <- 2        # run this many chains

# define the priors
priors <- list()
priors$R <- 1 * diag(2)
priors$k <- 2
priors$tau.mu <- 1.0E-3

snakes.post <- siberMVN(siber.snakes, parms, priors)#fitting multivariate normal model and getting                                                          posteriors

SEA.B_snakes <- siberEllipses(snakes.post)#estimating standard ellipse area from posteriors

means.B_snakes <- extractPosteriorMeans(siber.snakes, snakes.post)#mean isotope values

ccc <- names(snakes.post)

colnames(SEA.B_snakes) <- ccc

SEA.B_snakesdf = data.frame(SEA.B_snakes, check.names = F)%>%
  rowid_to_column(var = "run")%>%
  gather(Species.Tissue, SEA.B, -run)%>%
  separate(Species.Tissue, c("Species","Tissue"), sep = "([\\.\\?\\:])")

```

```{r}
#Summarising SEA estimates

SEA.B_snakesdf%>%
  group_by(Species, Tissue)%>%
  summarise(SEA.mean = mean(SEA.B),
            SEA.sd = sd(SEA.B),
            SEA.se = sd(SEA.B)/sqrt(n()))

```

### Testing difference in species niche area by tissue type

```{r}
SEA.B_snakesdf%>%
  spread(key = Species, value = SEA.B)%>%
  group_by(Tissue)%>%
  summarise(p = sum(`Hydrophis schistosus` > `Hydrophis curtus`)/n())
```

Hyp: *H. schistosus* SEA is larger than *H. curtus*
  
  While niche width is slightly larger in *H. schistosus*, it is not significantly different. The posterior distribution of SEA^~b~ has right skewed long tail (masked by the limits of the graph for visual clarity) possibly due to the low sample size. Niche width doesn't seem to change accross different tissue types either, indicating stability over variying periods of assimilation.


## Visualising posterior ellipses to compare species isotopic niche

```{r}
# how many of the posterior draws do you want?
n.posts <- 10

# decide how big an ellipse you want to draw
p.ell <- pchisq(1,2)

set.seed(1)

# a list to store the results
snake_ellipses <- list()

# loop over groups
for (i in 1:length(snakes.post)#sgenerating list with length groups*communities
){
  
  # a dummy variable to build in the loop
  ell <- NULL
  post.id <- NULL
  
  for ( j in sample(1:4000, n.posts)){#randomlu extracting parameters for n samples from posterior distribution
    
    # covariance matrix
    Sigma  <- matrix(snakes.post[[i]][j,1:4], 2, 2)
    
    # mean
    mu     <- snakes.post[[i]][j,5:6]
    
    # ellipse points
    
    out <- ellipse::ellipse(Sigma, centre = mu , level = p.ell)
    
    
    ell <- rbind(ell, out) #ellipse points from current loop
    post.id <- c(post.id, rep(j, nrow(out))) #adding loop number (rep)
    
  }
  ell <- as.data.frame(ell) # data frame of ellipse points from all draws
  ell$rep <- post.id #adding draw id
  snake_ellipses[[i]] <- ell #creading list of draws from each community.group
}

snake.ellipses <- bind_rows(snake_ellipses, .id = "id")#creating a data frame of post ellipse draws


# now we need the group and community names

# extract them from the ellipses.posterior list
group_comm_names <- names(snakes.post)[as.numeric(snake.ellipses$id)]#extractin communit.group from posteriors

# split them and conver to a matrix, NB byrow = T
split_group_comm <- matrix(unlist(strsplit(group_comm_names, "[.]")),
                           nrow(snake.ellipses), 2, byrow = TRUE)#splitting communit and group

snake.ellipses$community <- split_group_comm[,1]
snake.ellipses$group     <- split_group_comm[,2]

snake.ellipses <- dplyr::rename(snake.ellipses, iso1 = x, iso2 = y, 
                                Species = community, Tissue = group)

#Plotting 10 randomly sampled ellipses

siber_snakes%>%
  rename(Species = community,
         Tissue = group)%>%
  ggplot(aes(iso1, iso2, col = Species))+
  geom_point(aes(shape = Species), size = 2)+
  ylab(expression(paste(delta^{15}, "N (\u2030)")))+
  xlab(expression(paste(delta^{13}, "C (\u2030)")))+
  geom_polygon(data = snake.ellipses,
               mapping = aes(iso1, iso2, group = rep, linetype = Species, col = Species),
               fill = NA)+
  scale_color_brewer(palette = "Set1", direction = -1)+
  scale_fill_brewer(palette = "Set1", direction = -1)+
  facet_wrap(~Tissue)+
  theme(legend.text = element_text(face = "italic"))

ggsave(last_plot(), filename = "../Figures and Tables/figure3.tiff", height = 4.5, width = 8)
```

As seen in the SEA estimation, low sample size for *H. curtus* causes greater uncertainty in the estimation of standar ellipses even with bayesian inference. Both carbon and nitrogen isotpes seem to be enriched in scales when compared to plasma. Degree of overlap appears to be low for both tissues.

- Samples sizes for *H. curtus* in both tissues need to be increased despite using bayesian methods
- **Unusual outlier** in *H. schistosus* scales data needs to be checked

## Relative overlap in bayesian standard ellipses

```{r, cache = TRUE}
#Overlap in ellipse based on plasma samples
snake.p.overlap <- bayesianOverlap(ellipse1 = "Hydrophis schistosus.Plasma" , #Group 1
                                   ellipse2 = "Hydrophis curtus.Plasma", #Group 2
                                   snakes.post, #list with posteriour dists
                                   draws = 100, p.interval = 0.95, n = 100) #params

snake.p.overlap <- snake.p.overlap%>%
  mutate(Turnover = "Short-term")

#overlap in ellipse based on scale samples
snake.s.overlap <- bayesianOverlap(ellipse1 = "Hydrophis schistosus.Scales" , #Group 1
                                   ellipse2 = "Hydrophis curtus.Scales", #Group 2
                                   snakes.post, #list with posteriour dists
                                   draws = 100, p.interval = 0.95, n = 100) #params

snake.s.overlap <- snake.s.overlap%>%
  mutate(Turnover = "Long-term")

snake.overlap <- bind_rows(snake.p.overlap, snake.s.overlap)

snake.overlap%>%
  mutate(prop.overlap = overlap/(area1 + area2 - overlap))%>% #relative overlap
  ggplot(aes(prop.overlap))+
  geom_histogram(bins = 10, col = "black")+
  #geom_vline(aes(xintercept = mean(prop.overlap),  col = "red"), size = 1)+
  labs(x = "Proportion of overlap", y = "Number of samples")+
  scale_color_discrete(name = "Mean")+
  facet_wrap(~Turnover)
```

```{r}
snake.overlap%>%
  group_by(Turnover)%>%
  mutate(prop.overlap = overlap/(area1 + area2 - overlap))%>%
  summarise(Avg.overlap = mean(prop.overlap),
            sd = sd(prop.overlap))
```

Overlap between *H. curtus* and *H. schistosus* seems to be high in when comparing long term resource use, i.e., scales.

However, overlap between *H. curtus* and *H. schistosus* seems to be very low when comparing short term resource use, i.e., plasma.

This difference could be caused by:

- low sample size for *H. curtus*
- differences in processing of scales and plasma, i.e., lipid extraction
